---
title: "Developing Data Products Week 4"
date: "May 20, 2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Application description

This application predicts the price of a diamond based on its carat and cut. To use this app, we simply need to use the slider to select a carat value between 0 and 5, and choose a type of cut (*Fair, Good, Very Good, Premium*, or *Ideal*)

## UI Code

The following code was used to create the ui.R document. It creates a slider for the carat value and a dropdown for the cut type. Then in the main panel, it displays the plot and prediction of price by carat and highlights the cut of interest.

```{r, echo=TRUE, eval=FALSE}
library(shiny)
library(shinyWidgets)
library(ggplot2)

shinyUI(fluidPage(
        titlePanel("Predict Price of Diamond from Carat and Cut"),
        sidebarLayout(
                sidebarPanel(
                        sliderInput("slidercarat",
                                    "How many carats?", 0, 5.5, value = 0, step = .25, round = FALSE),
                        selectInput("slidercut", "What is the diamond cut?",
                                    choices = c("Fair", "Good", "Very Good", "Premium", "Ideal"))),
                submitButton("Submit")
        ),
        mainPanel(
                plotOutput("Plot"),
                h3("Predicted Diamond Price"),
                textOutput("pred")
        )
)
)
```

## Server Code

The following code was used to create the server.R document. It creates regression model to predict the price of a diamond by its carat and cut type.
```{r cars, echo = TRUE, eval=FALSE}
library(shiny)
library(ggplot2)
library(gghighlight)
data(diamonds)

shinyServer(function(input, output) {
        modelpred <- reactive({
                cutsub <-subset(diamonds, cut==input$slidercut)
                model <- lm(price ~ carat, cutsub)
                caratinput <- input$slidercarat
                predict(model, newdata=data.frame(carat=caratinput))
        })
        
        output$Plot <- renderPlot({
                cutinput <- input$slidercut
                cutsub <-subset(diamonds, cut==input$slidercut)
                g <- ggplot(diamonds, aes(x=carat, y=price, color=cut)) +
                        geom_point() + 
                        gghighlight(diamonds$cut == cutinput, label_key=cut) + 
                        geom_smooth(aes(x=cutsub$carat, y=cutsub$price),
                                    method="lm", col="purple") +
                        geom_point(aes(x=cutsub$carat, y=cutsub$price), colour="purple")
                g
        })
        
        output$pred <- renderText({
                paste(c(round(modelpred(),2),"$"))
        })
})
```

## Relevant Links

The Application can be found here: <http://jramil.shinyapps.io/MyFirstApp/>.

The complete code used to create this application can be found here:
<http://github.com/joanneramil/DevelopingDataProducts>
